%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Antonín }{Haas}{opensource enthusiast \& developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
Okružní~255
Jevíčko,~569~43
Czech Republic
~
+420~776~053~847
\href{mailto:tondahaas@gmail.com}{tondahaas@gmail.com}
~
\href{https://github.com/tuxanek}{github.com/tuxanek}
~
\href{https://flickr.com/tondahaas}{flickr.com/tondahaas}
\section{Languages}
Czech as native language
English (B2)
\section{Programming}
%{\color{red} $\varheart$} Python $\varheartsuit$
%{\color{red} $\varheartsuit$} Java, 
Java, C/C++, C\#, Python
HTML, CSS
LaTeX, Bash, Git
\section{Software}
Debian, Arch
\section{Driving licence}
none
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

\entry
{2015-now}
{Master {\normalfont of Computer Science}}
{Palacký University, Olomouc}
{\emph{Steganographic Methods} \\ Goal of the thesis is to determine, if there is a useful usage of fuzzy logic in steganography.}

\entry
{2012--2015}
{Bachelor {\normalfont of Computer Science}}
{Palacký University, Olomouc}
{\emph{Top-down Syntax Analysis} \\ This thesis demonstrate top-down syntax analysis based upon context-free grammar and pushdown automata.}

\entry
{2008--2012}
{{\normalfont High school}}
{Gymnázium Jevíčko}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
%\subsection{Full Time}

\subsection{Part Time}
\begin{entrylist}

\entry
{2013--now}
{Palacky University}
{Olomouc, Czech Republic}
{\emph{Network Administrator} \\
Technical support for students at dormitories. Helping with configuring ethernet and wireless settings in various OS and installing drivers.}

\entry
{2015--2016}
{CUTTER Systems spol. s r.o.}
{Prostějov, Czech Republic}
{\emph{Firmware Developer} \\
Developing FW for various microprocessors (PIC, AVR, ARM) in C language. Dealing with network communication, managing sensors data, packet routing, battery powered devices etc.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{entrylist}
\entry
{2016--now}
{\href{https://tux.inf.upol.cz}{Tux}}
{Univerzita Palackého, Olomouc}
{Student's linux server administrator}

\entry
{2012--2015}
{Ateneo}
{Univerzita Palackého, Olomouc}
{Chamber choir: bass.}

\entry
{2013, 2015}
{Redbot}
{Brno, Czech Republic}
{Participating in Red Hat programming competition.}

\entry
{2012}
{AMAVET competition}
{Prague, Czech Republic}
{High scool scientific project: Constuction of a linear pump (titrator).}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{Professional:} programming, GNU/Linux, opensource, Raspberry Pi
\\
\textbf{Personal:} music, chamber choir, analog \& digital photography

%----------------------------------------------------------------------------------------

\end{document}
